An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-24 Revision/response.tex

\textbf{Regarding dataset scale and scalability:}

We conducted experiments on a 100M-scale deep dataset and analyzed the performance of each algorithm on the large dataset. Please refer to MR.R7.

\textbf{Regarding the experimental parameter settings:}

For datasets with recommended parameters provided in the original papers, we directly used those recommended settings. For other datasets, we selected the parameter combinations that performed best through empirical evaluation. All parameters used in the experiments are available in our public code repository.

### 2025-07-24 Revision/response.tex

\textbf{Regarding index partitioning and merging:}

For partitioning and merging, only Filtered-DiskANN, which supports disk storage, builds indices separately and then merges them. However, the algorithms we focused on and evaluated in this study (with the exception of Filtered-DiskANN) are all designed and implemented based on in-memory index construction. Therefore, for the vast majority of algorithms, index partitioning and merging are not involved, which differs from DiskANN's design considerations.

\textbf{Regarding quantization time in index build:}

Of all the evaluated algorithms, Faiss, Puck, DiskANN, and Milvus support quantization. However, in our experiments, we did not enable quantization in any of our experiments. Therefore, no quantization time was included in the reported index build times.

### 2025-07-24 Revision/response.tex

\noindent
\textbf{Response:} 
Thank you for the suggestion. Since there are multiple methods, listing all URLs in Section 4.1 would be overwhelming. Instead, in Section 3, we add superscript markers next to each algorithm name and provide the corresponding implementation URLs as footnotes on the same page. (Please see the relevant footnotes in Section 3 in the revised manuscript)

\section*{Response to Review 3}
\setcounter{weakness}{0}

%%%%%%%%%%%%%%%%%%%%%% W1 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{weakness}
		\textit{Scalability experiments are missing; largest dataset is 10M; some pitfalls will only show at large scale.}
	\end{weakness}
}

\noindent
\textbf{Response:} 
Thank you for your suggestion. We have added experiments on the Deep100M dataset in Section 4.2.4 and Section 4.3.4, and we observed some pitfalls. For more details, please refer to our response to Meta Review R7.

### 2025-07-24 VLDB2026/main.tex
1

	%Similar to the evaluation of \textit{Attribute Filtering} algorithms, 
	Similarly, we also evaluate \textcolor{orange}{4} key metrics mentioned above in \textit{Range Filtering} algorithms. 
%	\textcolor{orange}{For the YT-Audio dataset with synthetic attributes and the YT-Audio dataset with real attributes, we can found that the data for index construction is basically the same, indicating that the authenticity of the attribute has almost no effect on index construction.However, the WIT dataset with synthetic labels is 2048-dimensional, while the WIT-Real dataset with real labels is 512-dimensional, so the dimension will cause a big difference.}

	\textit{\textbf{Index construction time.}}
	Figure~\ref{fig:rangeFilter_build_time} shows the single-threaded index construction time. Faiss builds the index fastest. As Faiss obtains subsamples through sampling and calculates the cluster centroid, the computational complexity is significantly reduced.
	%	shows the single-threaded index construction time. Faiss builds the index fastest. Because Faiss obtains subsamples through sampling and then calculates the cluster centroid, the computational complexity is significantly reduced.

@@

			\textbf{Large-Scale Dataset} & H & H & L & L &\textbf{H} &H  &M  &H  &M  &H  &\textbf{H}  &M/L  &L/M  &L/L  &M/M  &-  \\
			\textbf{Rare Attribute \& Low Range} &M  &M  &H  &H &\textbf{H}  &H  &H  &H  &L  &M  &\textbf{H} &M/M  &M/M  &L/L  &L/L  &L/L  \\
			\textbf{Robust to MultiModal Dataset} &H  &H  &L  &H  &\textbf{H}  &L  &M  &H  &M  &H  &\textbf{H}  &H/H  &M/M  &L/L  &L/L  &-/-  \\
			\textbf{Robust to Attribute Distribution} &L  &L  &H  &H  &H  &H  &-  &-  &-  &-  &-  &H/-  &L/-  &\textbf{H}/-  &L/-  &L/-  \\
			\textbf{High LID Dataset} &H  &M  &H  &M  &\textbf{H}  &M  &M  &H  &M  &H  &\textbf{H}  &L/L  &M/H  &L/L  &L/M  &L/L  \\
			\textbf{General-Purpose} &\faCheck  &\faCheck  &\faTimes  &\faTimes  &\faCheck  &\faTimes  &\faTimes  &\faCheck &\faTimes  & \faTimes &\faCheck&\faTimes  &\faCheck  &\faCheck  &\faTimes &\faTimes  \\
			\hline
		\end{tabular}
	}
	\centering
\end{table*}

>>>>

	%Similar to the evaluation of \textit{Attribute Filtering} algorithms, 
	Similarly, we also evaluate \textcolor{orange}{4} key metrics mentioned above in \textit{Range Filtering} algorithms. \textcolor{orange}{Note: For regular-scale datasets, all algorithms build indexes using a single thread. For the large-scale dataset Deep100M, all algorithms use 64 threads for index construction to improve efficiency, except DSG, which only supports single-threaded construction.}
%	\textcolor{orange}{For the YT-Audio dataset with synthetic attributes and the YT-Audio dataset with real attributes, we can found that the data for index construction is basically the same, indicating that the authenticity of the attribute has almost no effect on index construction.However, the WIT dataset with synthetic labels is 2048-dimensional, while the WIT-Real dataset with real labels is 512-dimensional, so the dimension will cause a big difference.}

	\textit{\textbf{Index construction time.}}
%	Figure~\ref{fig:rangeFilter_build_time} shows the single-threaded index construction time. 
	As shown in the Figure~\ref{fig:rangeFilter_build_time}, for regular-scale datasets, Faiss builds the index fastest. As Faiss obtains subsamples through sampling and calculates the cluster centroid, the computational complexity is significantly reduced.

@@

			\textbf{Large-Scale Dataset} & H & H & L & L &\textbf{H} &H  &M  &H  &M  &H  &\textbf{H}  &M/L  &L/M  &L/L  &M/M  &-  \\
			\textbf{Rare Attribute \& Low Range} &M  &M  &H  &H &\textbf{H}  &H  &H  &H  &L  &M  &\textbf{H} &M/M  &M/M  &L/L  &L/L  &L/L  \\
			\textbf{Robust to MultiModal Dataset} &H  &H  &L  &H  &\textbf{H}  &L  &M  &H  &M  &H  &\textbf{H}  &H/H  &M/M  &L/L  &L/L  &-/-  \\
			\textbf{Robust to Attribute Distribution} &L  &L  &H  &H  &H  &H  &-  &-  &-  &-  &-  &H/-  &L/-  &\textbf{H}/-  &L/-  &L/-  \\
			\textbf{High LID Dataset} &H  &M  &H  &M  &\textbf{H}  &M  &M  &H  &M  &H  &\textbf{H}  &L/L  &M/H  &L/L  &L/M  &L/L  \\
			\textbf{General-Purpose} &\faCheck  &\faCheck  &\faTimes  &\faTimes  &\faCheck  &\faTimes  &\faTimes  &\faTimes &\faTimes  & \faCheck &\faCheck&\faTimes  &\faCheck  &\faCheck  &\faCheck&\faTimes  \\
			\hline
		\end{tabular}
	}
	\centering
\end{table*}
